RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-06 paper_resources/doc/paper.tex
Introduction: update

	The problem of symbolic regression (SR)~\cite{billard2002symbolic} has attracted many researchers over the last decade to study it intensively. SR can be seen as a generalization of the well-known concept of linear regression, i.e., polynomial regression~\cite{stimson1978interpreting}. All regression models in principle have the same task: given a set of $n$-dimensional input data and the output data, the aim is to find a  mathematical expression (function) consisting of $n$ (input) variables that fit the output data w.r.t. some in advance known measure.  This computationally intensive task is in general provenly NP--hard~\cite{virgolin2022symbolic}. When aiming a model to be a linear combination of input variables, it represents the problem of linear regression. However, when there are some nonlinear relations between variables, which are relevant, linear regression models are not enough. This is the point where symbolic regression comes into play. Unlike linear regression, it allows the search over the space of all possible mathematical formulas to find the best-fitting ones able to predict the output variable from the input variables. The basis of constructing the explicit formula is the basic operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and other elementary functions.  \fxnote{Marko: došao dovde sa ovom sekcijom}
	%Application: https://towardsdatascience.com/real-world-applications-of-symbolic-regression-2025d17b88ef

	 Concrete examples of application of SR include having a less black--box tool, as it may say much more how SR model achieve predictions, that is the coefficients and functions that build the model may indicate on larger importance of some variables over the others. Moreover, in that way we may grasp why the variables are related in the obtained way. As an example, appearance of an exponential function may associate  to  some physical phenomenon such as intensity of radiation or acceleration over time, see~\cite{udrescu2020ai}. Additionally, the SR models, if they are correct, may have    posses  larger extrapolation power than other mathematical models, and especially than neural network--based methods. SR models may maximize obtaining physically more reasonable equations that could serve as insight towards  establishing  physical theory behind as the final goal.  Practical applications of SR in chemical and biological sciences are listed in~\cite{weng2020simple}. In particular,  the discovery of a series of new oxide perovskite catalysts with improved activities is presented there. Applications of SR to discovering physical laws from distorted video is studied in~\cite{udrescu2021symbolic} by means of a unsupervised learning method. Revealing complex ecological dynamics by SR is presented in~\cite{chen2019revealing}, tackled by  a machine learning method. Application of SR to model the mutations effects on protein  stability, in the domain of fundamental and applied biology,  is shown in~\cite{louis2021reviewing}. One of the recent work studies of  auto-discovering conserved quantities using trajectory data from unknown dynamical systems, where SR is solved by a machine learning algorithm, see~\cite{liu2021machine}. Last but not least, we mention the paper~\cite{liang2019phillips} discovers  the application of  SR to model analytic representations of the exciton binding energy. The use of solving the SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic,kabliman2021application}. Yet another application to wind speed forecasting is given in~\cite{abdellaoui2021symbolic}.

>>>>

	The problem of symbolic regression (SR)~\cite{billard2002symbolic} has attracted many researchers over the last decade to study it intensively. SR can be seen as a generalization of the well-known concept of linear regression, i.e., polynomial regression~\cite{stimson1978interpreting}. All regression models in principle have the same task: given a set of $n$-dimensional input data and the output data, the aim is to find a  mathematical expression (function) consisting of $n$ (input) variables that fit the output data w.r.t. some in advance known measure.  This computationally intensive task is in general provenly NP--hard~\cite{virgolin2022symbolic}. When aiming a model to be a linear combination of input variables, it represents the problem of linear regression. However, when there are some nonlinear relations between variables, which are relevant, linear regression models are not enough. This is the point where symbolic regression comes into play. Unlike linear regression, it allows the search over the space of all possible mathematical formulas to find the best-fitting ones able to predict the output variable from the input variables. The basis of constructing the explicit formula is the basic operations like addition and multiplication, as well as polynomial, trigonometric, exponential, and other elementary functions.  
	%Application: https://towardsdatascience.com/real-world-applications-of-symbolic-regression-2025d17b88ef

	Concrete examples of the application of SR include having a less black--box tool, as it may say more about how the SR model achieves predictions, that is the coefficients and functions that build the model may indicate on larger importance of some variables over the others. Moreover, in that way, we may grasp why the variables are related in the obtained way. As an example, the appearance of an exponential function may associate with some physical phenomenon such as the intensity of radiation or acceleration over time, see~\cite{udrescu2020ai}. Additionally, the SR models, if they are correct, may possess larger extrapolation power than other mathematical models, especially better from the neural network--based methods. SR models may maximize obtaining physically more reasonable equations that could serve as an insight towards establishing physical theory behind as the final goal.  Practical applications of SR in chemical and biological sciences are listed in~\cite{weng2020simple}. In particular,  the discovery of a series of new oxide perovskite catalysts with improved activities is presented there. The application of SR to discovering physical laws from a distorted video is studied in~\cite{udrescu2021symbolic} by means of an unsupervised learning method. Revealing complex ecological dynamics by SR is presented in~\cite{chen2019revealing}, tackled by a machine learning method. Application of SR to model the effects of the mutations on protein stability, in the domain of fundamental and applied biology,  is shown in~\cite{louis2021reviewing}. One of the recent work studies of auto-discovering conserved quantities using trajectory data from unknown dynamical systems, where SR is solved by a machine learning algorithm, see~\cite{liu2021machine}. Last but not least, we mention the paper~\cite{liang2019phillips} discovers the application of  SR to model analytic representations of the exciton binding energy. The use of solving the SR in material science is described in~\cite{wang2019symbolic,wang2022symbolic,burlacu2022symbolic,kabliman2021application}. Yet another application to wind speed forecasting is given in~\cite{abdellaoui2021symbolic}.

	\fxnote{Marko: došao dovde sa ovom sekcijom}
